SUPPORTING INFORMATION:\\ Headgroup Structure and Cation Binding in Phosphatidylserine Lipid Bilayers

### 2019-09-12 Manuscript/manuscriptPSsuppl.tex
Update to the submitted revised version

\noindent
{\it Josef Melcr}
prepared tools for calculating order parameters, performed Lipid14/17 simulations with Gromacs MD simulation package,
prepared the TOC figure and provided comments on the manuscript.

@@

\noindent
{\it Jukka M{\"a}{\"a}tt{\"a}}
Did minor analysis for and edited Figures 6 and 10.

>>>>

\noindent
{\it Josef Melcr}
prepared tools for calculating order parameters, performed Lipid14/17 simulations with Gromacs MD simulation package,
and provided comments on the manuscript.

@@

\noindent
{\it Jukka M{\"a}{\"a}tt{\"a}}
Prepared figures 6 and 10.
